Case study validations of automatic bullet matching

### 2018-11-06 index.Rmd
percentage sign messed up formatting

One of the measures used by firearms examiners to describe the strength of a match quantitatively is the number of consecutive matching striae (CMS) as defined by \citet{biasotti}.
If there are at least 6 consecutive matching striae, the bullets are considered to be a good match \citep{biasotti_firearms_1997,nichols_scientific_2006}, according to criteria used by FTEs. 
CMS in this setting are counted as the number of consecutive peaks in signatures of two lands that match.

\hh{HH: let's not go into what we do not do, and instead focus on what we do}
~~  There are some differences between CMS as defined by FTEs and the method used in \citet{aoas} includes both peaks and valleys, as it is easier to assess the features separately using cross-sections. XXX Should we go into this, or just leave it as is?~~

@@

@@

```{r eer, fig.cap="Equal Error Rates for all measures (RF score, Cross-correlation and CMS) under all five (sub-)studies. CMS is signifcantly worse than both Cross-correlation and the RF score. At best, Cross-correlation and RF score have errors for land-to-land comparison of around 5%.", out.width = '.5\\textwidth'}
aucs %>% ggplot(aes(y = studyg, x = eer, colour=measure, shape = measure)) + 
  geom_point(size = 3) +theme_bw() +
  xlim(c(0, .35)) +
  xlab("Equal Error Rates (EER)") +
  ylab("") +
  scale_color_brewer(palette = "Set2")
```

>>>>

@@

\hh{maximum cross-correlation is determined for aligning two signatures [@aoas, @vorburgerApplicationsCrosscorrelationFunctions2011]}

One of the measures used by firearms examiners to describe the strength of a match quantitatively is the number of consecutive matching striae (CMS) as defined by \citet{biasotti}.
If there are at least 6 consecutive matching striae, the bullets are considered to be a good match \citep{biasotti_firearms_1997,nichols_scientific_2006}, according to criteria used by FTEs. 
CMS in this setting are counted as the number of consecutive peaks in signatures of two lands that match. 
\hh{Note that because signatures are moved into phase based on the maximum cross-correlation rather than matching striation marks. This can result in a consecutive matching striae of 0. }

@@

```{r eer, fig.cap="Equal Error Rates for all measures (RF score, Cross-correlation and CMS) under all five (sub-)studies. CMS is signifcantly worse than both Cross-correlation and the RF score. At best, Cross-correlation and RF score have errors for land-to-land comparison of around 5\\%.", out.width = '.5\\textwidth'}
aucs %>% ggplot(aes(y = studyg, x = eer, colour=measure, shape = measure)) + 
  geom_point(size = 3) +theme_bw() +
  xlim(c(0, .35)) +
  xlab("Equal Error Rates (EER)") +
  ylab("") +
  scale_color_brewer(palette = "Set2")
```
